CSD, Disjoint components and trayectory detection

### 2019-11-20 ArticuloCSDyCM/Paper03.tex
Cuadernos separados para trazos

\subsection{Application to evoked activity in idem.}\label{sec:evocada}

@@

The facilitated activity through a small injury produces very clean
and ordered activity in the CA layers, as measured by the CM analysis.
The results can be seen in the figures
\ref{diagfaci}, \ref{lfpcsdcmfaci}, \ref{facitracks} and
\ref{facitracktodas}.
A previous diagram is on the figure \ref{diagfaci}.

@@

@@

\subsection{Application to epileptic-like activity in the hippocampus}
This is probably the most complicated data, 
numerically and qualitatively, which comes from a series of epileptic burst
that occurred after 15 minutes of application of 4AP to living slices of
hippocampus. Each burst occurs with activity spreading over many sites almost
simultaneously. This turned out to be a test of the applicability and
robustness of our method.
The necessity of having a good error value for the inactive set was more apparent here
than in the other cases. Also, the most striking features of the propagation of activity,
coded now as trajectories of the CM, could be seen here, as the epileptic burst covered the whole
CA structure. A sample of the raw data in $\muV{}$ can be seen in the figure \ref{lfpycsd4ap}.
Five key moments in the epileptic burst have been selected, one just before the onset of the attack, the next one at the peak and one  following it, and the last at the subsiding moments. The figure compares the Raw data
in $\muV{}$ in the first row, then the raw CSD representation in the second row, and
in the third raw a CSD after a Gaussian Blur Filter has been applied,
with a $\sigma$ value of $ \mum{42}$. After the Gaussian Blur acts a sort of
spatial denoising mechanism, the disjoint components are apparent to the eye.
In the figure \ref{csdfrontera} we apply the border criterion for the disconnected
components. Again, in the first row we have the CSD without the Gaussian Blur.
Even though well localized patches of activity are to be seen over the
stratum pyramidale, large parts of the activity remain hidden by the noise.
After the Gaussian Blur has been applied the joint sets of activity are evident.

@@

>>>>

\subsection{Application to evoked activity in the rat's hippocampus}\label{sec:evocada}

@@

The facilitated activity through a small injury produces very clean
and ordered activity in the CA layers, as measured by the CM analysis.
The results can be seen in the figures
\ref{diagfaci}, \ref{lfpcsdcmfaci}, \ref{facitracks} and
\ref{facitracktodas}.
A previous diagram is on the figure \ref{diagfaci}, and some
exemplary traces in the figure \ref{trazfaci}.

@@

\begin{figure}[H]
   \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{Figuras/mapstddfaci.pdf}
        \caption{Location of electrodes}
        \label{maptrazfaci:map}
    \end{subfigure}
    \qquad
    %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[t]{0.15\textwidth}
        \includegraphics[width=\textwidth]{Figuras/trazoselectfaci.pdf}
        \caption{Traces}
        \label{maptrazfaci:traz}
    \end{subfigure}
    \caption{
      \begin{intension}
        Mostrar los trazos en variar regiones del hipocampo para
        aclarar el suceso del ataque epiléptico.
      \end{intension} 
      A selection of traces of the recordings for various electrodes.
      In the subfigure \ref{maptrazfaci:map}, the selected electrodes
      are shown against the standard deviation of the recording of the
      potential, which gives a good indication of the more active
      sites, and therefore, of the structure of the hippocampus.
      The electrode labeled ``a'' is over CA3 proximal, on the other
      extreme ``h'' is in the middle of CA1.
    }\label{trazfaci}
\end{figure}

@@

\subsection{Application to epileptic-like activity in the hippocampus}

This is probably the most complicated data, 
numerically and qualitatively, which comes from a series of epileptic burst
that occurred after 15 minutes of application of 4AP to living slices of
hippocampus. Each burst occurs with activity spreading over many sites almost
simultaneously. This turned out to be a test of the applicability and
robustness of our method.
The necessity of having a good error value for the inactive set was more apparent here
than in the other cases. Also, the most striking features of the propagation of activity,
coded now as trajectories of the CM, could be seen here, as the epileptic burst covered the whole
CA structure. A sample of the raw data in $\muV{}$ can be seen in the figure \ref{lfpycsd4ap}. In the figure \ref{traz4ap} some exemplarly traces
can be seen.
Five key moments in the epileptic burst have been selected, one just before the onset of the attack, the next one at the peak and one  following it, and the last at the subsiding moments. The figure compares the Raw data
in $\muV{}$ in the first row, then the raw CSD representation in the second row, and
in the third raw a CSD after a Gaussian Blur Filter has been applied,
with a $\sigma$ value of $ \mum{42}$. After the Gaussian Blur acts a sort of
spatial denoising mechanism, the disjoint components are apparent to the eye.
In the figure \ref{csdfrontera} we apply the border criterion for the disconnected
components. Again, in the first row we have the CSD without the Gaussian Blur.
Even though well localized patches of activity are to be seen over the
stratum pyramidale, large parts of the activity remain hidden by the noise.
After the Gaussian Blur has been applied the joint sets of activity are evident.

@@

\begin{figure}[H]
   \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{Figuras/mapstdd4AP.pdf}
        \caption{Location of electrodes}
        \label{maptraz4ap:map}
    \end{subfigure}
    \qquad
    %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[t]{0.15\textwidth}
        \includegraphics[width=\textwidth]{Figuras/trazoselect4AP.pdf}
        \caption{Traces}
        \label{maptraz4ap:traz}
    \end{subfigure}
    \caption{
      \begin{intension}
        Mostrar los trazos en variar regiones del hipocampo para
        aclarar el suceso del ataque epiléptico.
      \end{intension} 
      A selection of traces of the recordings for various electrodes.
      In the subfigure \ref{maptraz4ap:map}, the selected electrodes
      are shown against the standard deviation of the recording of the
      potential, which gives a good indication of the more active
      sites, and therefore, of the structure of the hippocampus.
      The electrode labeled ``a'' is putatively over GD, while ``h''
      is in the medial CA1.}\label{traz4ap}
\end{figure}
